HERMES: Hybrid Error-corrector Model with inclusion of External Signals for nonstationary fashion time series

### 2023-07-22 tmlr_submission/hermes_paper_revision/hermes_paper.tex
update revised paper

Due to the increasing use of social media and continuous changes of users' behaviours, a normalization step is applied to the raw sequences $y^{c,g,m,\textcolor{orange}{j}}$ in order to remove bias. \textcolor{orange}{The pre-processing of data presented in this section does not constitute a technical contribution. We present this step in depth to clearly explain how fashion time series are constructed.} Let $\Tilde{y}^{c,g,m}$ be the global sequence of the cloth type $c$ for the gender $g$ on market $m$ (e.g the evolution of the skirts in general for female in Europe). With the R package \texttt{stats}, the Seasonal-Trend decomposition using LOESS  \citep{cleveland1990} is used to remove the seasonal component of $\Tilde{y}^{c,g,m}$. The resulting deseasonalized signal is called  $\bar{y}^{c,g,m}$. Finally, for any fashion trend $\textcolor{orange}{j}$, the following normalized sequence is defined for all $ 0 \leq t \leq T$:
\begin{equation}
    y^{i}_t = \frac{y^{c,g,m,\textcolor{orange}{j}}_{t}}{\bar{y}^{c,g,m}_t}\,,
\end{equation}

>>>>

Due to the increasing use of social media and continuous changes of users' behaviours, a normalization step is applied to the raw sequences $y^{c,g,m,\textcolor{orange}{j}}$ in order to remove bias. \textcolor{orange}{The pre-processing of data presented in this section does not constitute a technical contribution. This step is presented in depth to  explain how the dataset provided with this paper is constructed.} Let $\Tilde{y}^{c,g,m}$ be the global sequence of the cloth type $c$ for the gender $g$ on market $m$ (e.g the evolution of the skirts in general for female in Europe). With the R package \texttt{stats}, the Seasonal-Trend decomposition using LOESS  \citep{cleveland1990} is used to remove the seasonal component of $\Tilde{y}^{c,g,m}$. The resulting deseasonalized signal is called  $\bar{y}^{c,g,m}$. Finally, for any fashion trend $\textcolor{orange}{j}$, the following normalized sequence is defined for all $ 0 \leq t \leq T$:
\begin{equation}
    y^{i}_t = \frac{y^{c,g,m,\textcolor{orange}{j}}_{t}}{\bar{y}^{c,g,m}_t}\,,
\end{equation}
